\documentclass[11pt]{article}
 
\usepackage[text={6in,8.1in},centering]{geometry}
 
\usepackage{enumerate}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathrsfs} % to use mathscr fonts
 
\usepackage{pstricks}
\usepackage{pst-solides3d}
\usepackage{pstricks-add}
\usepackage{graphicx}
\usepackage{pst-tree}
\usepackage{pst-poly}
\usepackage{calc,ifthen}
\usepackage{float}\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\usepackage{tikz}
\usepackage{tkz-berge}
\usepackage{fancyhdr}
\usepackage{algorithmicx,algpseudocode}
\usepackage{changepage}
\usepackage{color}
\usepackage{listings}
\usepackage{fancyvrb}

\lstset{ %
language=C++,                % choose the language of the code
basicstyle=\footnotesize,       % the size of the fonts that are used for the code
numbers=none,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
frame=none,           % adds a frame around the code
tabsize=2,          % sets default tabsize to 2 spaces
captionpos=b,           % sets the caption-position to bottom
breaklines=true,        % sets automatic line breaking
breakatwhitespace=false,    % sets if automatic breaks should only happen at whitespace
escapeinside={\%*}          % if you want to add a comment within your code
}

\newenvironment{block}{\begin{adjustwidth}{1.5cm}{1.5cm}\noindent}{\end{adjustwidth}}

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
 
\title{Extremal Functions on Cayley Digraphs of\\ Finite Cyclic Groups\footnote{Supported in part by National Science Foundation (NSF).}}
\author{{\sc Jordan Blocher}\\ 
Department of Mathematics\\ 
University of Nevada-Reno\\ 
Reno, Nevada, USA\\
{\tt jordanblocher@gmail.com}
\and 
{\sc Samantha Hampton}\\
Department of Mathematics\\
University of Arkansas\\
Fayetteville, Arkansas, USA\\
{\tt smhampto@uark.edu}
\and 
{\sc Christopher Linden}\\
Department of Mathematics\\
University of California  at Los Angeles\\
Los Angeles, California, USA\\
{\tt lindenechris@gmail.com} }
\date{July 30, 2012}
 
 
\def\R{\mbox{$\mathbb R$}}
\def\Q{\mbox{$\mathbb Q$}}
\def\Z{\mbox{$\mathbb Z$}}
\def\N{\mbox{$\mathbb N$}}
\def\C{\mbox{$\mathbb C$}}
\def\Sym{\operatorname{Sym}}
\def\lcm{\operatorname{lcm}}
\def\adj{\operatorname{adj}}
\def\inc{\operatorname{inc}}
\def\Cay{\operatorname{Cay}}
\def\Geom{\operatorname{\cal G}}
\def\ker{\operatorname{ker}}
\def\kernel{\operatorname{ker}}
\def\automorphism{\operatorname{Aut}}
\def\endomorphism{\operatorname{End}}
\def\inner{\operatorname{Inn}}
\def\outer{\operatorname{Out}}
\def\crossing{\operatorname{cr}}
\def\cent{\textcent}
\def\n{\\ \vspace{1.7mm}}
\def\diam{\operatorname{diam}}

\renewcommand{\emptyset}{\O}
 
 
\newcounter{ZZZ}
\newcounter{XXX}
\newcounter{XX}
 
\headsep25pt\headheight20pt
 
 
\pagestyle{fancyplain}
\lhead{\fancyplain{}{\small\bfseries Blocher, Hampton, Linden,\ \ Cayley Digraphs of Finite Cyclic Groups}}
\rhead{\fancyplain{}{\small\bfseries\thepage}}
%\cfoot{\ \hfill\tiny\sl Draft printed on \today}
 
 
\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables
 
 
 
\begin{document}
 
\baselineskip6mm\parskip4mm

\maketitle

\begin{abstract}
For positive integers $d$ and $k$ we define $m(d,k)$ to be the maximum positive integer $m$ such that the \emph{Cayley digraph} $\Cay(\Z_{m}, \mathscr{A})$ of $\Z_{m}$ generated by a set $\mathscr{A}$ of $k$ positive integers   has diameter less than or equal to $d$, where $\Z_{m}$ is the finite cyclic group of residue classes modulo $m$.
In this paper we establish a new lower bound for $m(2, k)$, namely
\[
 m(2,k) \geq \frac{37}{121}k^2 + O(k)\qquad\text{as}\quad k\to\infty.
\]
In this paper, we  also use this lower bound to obtain a lower bound for  $m(d,k)$ for any given positive integer $d$:
\[
m(d,k) \geq \left(\frac{148}{121}\right)^{\lfloor \frac{d}{2}\rfloor}\left(\frac{k}{d}\right)^d + O(k^{d-1})\qquad\text{as}\quad k\to\infty.
\]
\end{abstract}
 
{\small\sc Keywords:} {\small Cayley Digraphs, Extremal Problems, Networks, Postage Stamp Problem}
 

\section{Introduction}
Let $\Gamma$ be a finite group with a subset $\mathscr{A}$. The \emph{Cayley digraph}, denoted Cay($\Gamma, \mathscr{A}$), is a digraph with vertex set $\Gamma$, such that ($x, y$) is a directed edge if and only if $yx^{-1}$ $\in$ $\mathscr{A}$.  If $\mathscr A$ is {\em symmetric}, i.e.\,, $a\in \mathscr A$ implies $a^{-1}\in \mathscr A$, then $\Cay(\Gamma,\mathscr A)$ can be considered as an undirected graph.  Let $\Z_{m}$ denote the finite cyclic group of residue classes modulo $m$.  For instance, the $n$-cube can be considered as the Cayley (undirected) graph of $\Z_{2}^{n}$ generated by 
\[
\mathscr {A}=\{\mathbf e_{1},\mathbf e_{2},\ldots,\mathbf e_{n}\}
\]
where $\mathbf e_{i}$ is the $i$th identity element of $\Z_{2}^{n}$. $n$-cubes have been  well-studied and they have often  used as a model for interconnection networks. The following Figure shows the Cayley graph of $\Z_{12}$ generated by $\mathscr A=\{1,6,11\}$.

\begin{figure}[h]
\begin{center}\scriptsize
\begin{tikzpicture}[scale=0.50]

\Vertex[x=187.5pt,y=337.5pt]{0};
\Vertex[x=262.5pt,y=317.4038105676658pt]{1};
\Vertex[x=317.4038105676658pt,y=262.5pt]{2};
\Vertex[x=337.5pt,y=187.5pt]{3};
\Vertex[x=317.4038105676658pt,y=112.50000000000004pt]{4};
\Vertex[x=262.5pt,y=57.596189432334185pt]{5};
\Vertex[x=187.50000000000003pt,y=37.5pt]{6};
\Vertex[x=112.50000000000004pt,y=57.596189432334185pt]{7};
\Vertex[x=57.59618943233425pt,y=112.49999999999991pt]{8};
\Vertex[x=37.5pt,y=187.49999999999997pt]{9};
\Vertex[x=57.59618943233421pt,y=262.5pt]{10};
\Vertex[x=112.49999999999994pt,y=317.4038105676658pt]{11};

\tikzset{EdgeStyle/.style={->}}

\Edge(0)(1)
\Edge(1)(2)
\Edge(2)(3)
\Edge(3)(4)
\Edge(4)(5)
\Edge(5)(6)
\Edge(6)(7)
\Edge(7)(8)
\Edge(8)(9)
\Edge(9)(10)
\Edge(10)(11)

\Edge(0)(11)
\Edge(1)(0)
\Edge(2)(1)
\Edge(3)(2)
\Edge(4)(3)
\Edge(5)(4)
\Edge(6)(5)
\Edge(7)(6)
\Edge(8)(7)
\Edge(9)(8)
\Edge(10)(9)
\Edge(11)(10)

\Edge(0)(6)
\Edge(1)(7)
\Edge(2)(8)
\Edge(3)(9)
\Edge(4)(10)
\Edge(5)(11)
\Edge(6)(0)
\Edge(7)(1)
\Edge(8)(2)
\Edge(9)(3)
\Edge(10)(4)
\Edge(11)(5)

\end{tikzpicture}
\caption{ $\Cay(\Z_{12}, \{1, 6, 11\})$.}
\end{center}
\end{figure}

Note that $\Cay(\Z_{12}, \{1, 6, 11\})$ has the same diameter and degree as the $3$-cube, but this graph contains $12$ vertices.  It is natural to ask for the maximum number of vertices a Cayley digraph could possibly have with given diameter and maximum degree.  We focus on this question in this paper.

Cayley digraphs $\Cay(\Z_{m},\mathscr A)$ of $\Z_{m}$ are called $\emph{circulant}$ (di)graphs.  In this paper, we focus on circulant graphs.  However, $n$-cubes may not be as efficient as circulant graphs of equal degree and diameter.  

 Cayley digraphs, and circulant graphs in particular are often used as models for interconnection networks. As such, it is naturally desirable to maximize the number of vertices which can be connected with constraints on diameter and degree.

For any positive integer $d$ we define
\[
m(d,\mathscr{A}) =\ \max\{m \  \vert \  \diam(Cay(m,\mathscr{A})) \leq d\},
\]
the largest positive integer $m$ such that the diameter, $d(m,\mathscr{A})$, of the Cayley digraph $Cay(m,\mathscr{A})$ is less than or equal to $d$. For positive integers $d$ and $k$,
\[
m(d, k) = \max_{\scriptstyle \mathscr{A}\subseteq\mathbb Z^{+}\atop\scriptstyle |\mathscr{A}|=k}\{m\  |\  \diam(Cay(m,\mathscr{A})) \leq d\}
\]
the maximum modulus $m$ such that there exists a generating set with cardinality equal to $k$ and the diameter of the Cayley digraph is less than or equal to $d$. 

It is clear that $m(1,k) = k+1$ and $m(d,1) = d+1$.
In 1974 Wong and Coppersmith \cite{Wong-Coppersmith:1974} proved that, for positive integers $d$ and $k$,
\[
\left \lfloor \frac dk + 1 \right \rfloor^k \leq m(d, k) \leq  \binom{k + d}k . 
\]
To see the the upper bound, let $|\mathscr{A}| = k$ such that $\diam(Cay(\Z_m, \mathscr{A})) \leq d$. Noting that every element in $\Z_m$ is the sum of at most $d$ not necessarily distinct elements of $\mathscr{A}$, and the commutativity of integers,  we see that
\[
m \leq \binom{k + 1 + d - 1}k = \binom{k + d}k,
\] 
thus proving the upper bound.
Let
\[t = \left \lfloor \frac{d}{k} \right \rfloor + 1\]
and 
\[A = \{1, t, t^2, ... , t^{k-1}\}.\]
For any $x \in [0, t^k -1]$ we have
\[x = \sum_{i=1}^{k - 1}c_it^i.\]
Since 
\[
\sum_{i=1}^{k} c_i \leq k(t - 1) = k \left \lfloor \frac dk \right \rfloor  \leq d,
\]
we see that $d(0, x) \leq d$. Hence, $\diam(Cay(\Z_{t^k}, \mathscr{A}) \leq d$. Thus we see
\[m(d, k) \geq t^k  = \left \lfloor \frac dk + 1 \right \rfloor^k.
\]

Hsu and Jia \cite{JiaHsu} proved that 
\begin{equation}\label{eqn:m(d,2)>27}
m(d,2) =\left \lfloor \frac{d(d+4)}{3}\right \rfloor+1
\end{equation}
for all $d\geq2$. 

It is easy to show that $m(2,k)\ge \frac14k^{2}+O(k)$ as $k\to\infty$.  The current best known lower bound for $m(2,k)$ is
\[
m(2,k)\ge\frac27k^{2}+O(k)\qquad\text{as}\quad k\to\infty.
\]
See last section for more information on this lower bound.
In this paper, we prove a non-trivial lower bound for $m(2,k)$ in the following theorem.

\begin{theorem}\label{thm:m(2k)}
$\displaystyle m(2,k) \geq \frac{37}{121}k^2 + O(k)$  as $ k \to \infty$.
\end{theorem}

\begin{theorem}\label{thm:m(dk)}
For any integer $d \geq 2$, as $k \to \infty$, we have 
\[
m(d,k) \geq \left(\frac{148}{121}\right)^{\lfloor \frac{d}{2}\rfloor}\left(\frac{k}{d}\right)^d + O(k^{d-1}).
\]
\end{theorem}
 
 
 
\section{Proof of Theorem~\ref{thm:m(2k)}}
 

Let $k \geq$ 14 be an integer. Let $\displaystyle k_1 = \left \lfloor \frac{k - 3}{11} \right \rfloor$. Let $m = 37k_1^2$.  Define 
\begin{align*}
I_\mu &= [\mu k_1^2, \mu k_1^2 + k_1],
&&\mu = 0, 4, 15, 26; \\
S_\nu &= \{\nu k_1^2 + ik_1 \ |\  i = 0 , 1, ... , k_1 - 1\},
&&\nu = 0, 1, 2, 3;\\
T_{\eta} &= \{\eta k_1^2+ i(k_1 + 1) \ |\   i = 0 , 1, ... , k_1 -1\},
&&\eta = 10, 20, 30.
\end{align*}
 Let $S= S_{0} \cup S_{1} \cup S_{2} \cup S_{3}$, and
define
\[
\mathscr{A}=I_0\cup I_4\cup I_{15}\cup I_{26}\cup S\cup T_{10}\cup T_{20}\cup T_{30}.
\]
Noting  that $I_0\cap S_0=\{0\}$, and 
\[
|I_\mu| = k_1 + 1,\quad 
|S_\nu| = k_1,\quad\text{and}\quad
|T_\eta| = k_1,
\]
we see that 
\[
|\mathscr{A|} \leq 11k_1 + 3 \leq k.
\]  
We now prove that $\mathscr{A}+\mathscr{A}=\Z_m$.
We begin by claiming $I_{\mu}+T_{\eta}\supseteq[(\mu + \eta )k_1^2 ,  (\mu + \eta  + 1)k_1^2)$. Let $n \in[(\mu + \eta )k_1^2 ,  (\mu + \eta  + 1)k_1^2)$.
Then we can write $n$ as 
\[
n = (\mu + \eta ) k_1^2 + qk_1 + r,
\]
where $0 \leq q < k_1$ and $0 \leq r < k_1$.

If $r \geq q$, then $0\le r-q<k_{1}$ and
\[
n = \mu k_1^2 +  (r - q)+ \eta k_1^2 + q(k_1+1).
\]
 Since 
 \[
 \mu k_1^2 + (r - q) \in I_\mu\qquad\text{and}\qquad \eta k_1^2 +q(k_1+1) \in T_\eta,
 \]
we see that $n \in I_{\mu}+T_{\eta}$. 

If $r < q$, then we must have $q \geq 1$ and $0\le k_{1}+r-q+1\le k_{1}$. Then
\[
\mu k_1^2 + (k_1 + r - q + 1) \in I_\mu \qquad \text{and}\qquad
\eta k_1^2 + (q - 1)(k_1 + 1) \in T_\eta.
\]
 Hence
\[
n = \mu k_1^2 + (k_1 + r - q + 1)+\eta k_1^2 + (q - 1)(k_1 + 1) \in I_{\mu}+T_{\eta}.
\]
 

Next we claim that  $I_{\mu}+S_{\nu}\supseteq[(\mu + \nu )k_1^2 ,  (\mu + \nu  + 1)k_1^2)$. Let $n \in[(\mu + \nu )k_1^2 ,  (\mu + \nu  + 1)k_1^2)$.
Then we can write $n$ as 
\[
n = (\mu + \nu ) k_1^2 + qk_1 + r = \mu k_1^2 + r+\nu k_1^2 + qk_1,
\]
where  $0 \leq q < k_1$ and $0 \leq r < k_1$, such that 
\[
\mu k_1^2 + r \in I_\mu \qquad\text{and}\qquad\nu k_1^2 + qk_1 \in S_\nu,
\]
 so $n \in I_{\mu}+S_{\nu}$. 

Our final claim is $S+T_\eta \supseteq[(\eta  +1)k_1^2 ,  (\eta  + 4)k_1^2)$.  Let $n \in[(\eta  +1)k_1^2 ,  (\eta  + 4)k_1^2)$.
Then we can write $n$ as 
\[
n = (\eta  + \nu ) k_1^2 + qk_1 + r, 
\]
where $1 \leq \nu  \leq 3$, $0 \leq q < k_1$, and $0 \leq r < k_1$. 

If $q \geq r$, then
\[
n = \nu k_1^2 + (q - r) k_1+\eta k_1^2 + r(k_1 + 1), 
\]
where $\nu k_1^2 + (q - r)k_1 \in S_\nu$ and $\eta k_1^2 + d(k_1 + 1) \in T_\eta$, so $n \in S_\nu +T_\eta$. 

If $q <r$, then
\[
n = (\nu  - 1)k_1^2 + (k_1 + q - r) k_1+\eta k_1^2 + r(k_1 + 1), 
\]
where 
\[
(\nu  - 1)k_1^2 + (k_1 + q - r)k_1 \in S_{\nu  - 1}\qquad\text{and}\qquad
\eta k_1^2 + r(k_1 + 1) \in T_\eta.
\]
Hence $n \in S_{\nu-1}+T_\eta\subseteq S+T_{\eta}$. 
It is clear that, in $\Z_{37k_{1}^{2}}$,
\begin{align*}
[45k_{1}^{2},46k_{1}^{2})&=[8k_1^2, 9k_1^2),\\
[46k_{1}^{2},47k_{1}^{2})&=[9k_1^2, 10k_1^2),\\
[56k_{1}^{2},57k_{1}^{2})&=[19k_1^2, 20k_1^2).
\end{align*}
Therefore, we have proved that the entire interval $[0, m)=\Z_{m}$ can be  {\em covered\/} as follows: 
\begin{align*}
I_0 + S  &\supseteq [0, 4k_1^2),\\
I_4 + S  &\supseteq [4k_1^2, 8k_1^2),\\
I_{15} + T_{30}  &\supseteq[45k_{1}^{2},46k_{1}^{2})= [8k_1^2, 9k_1^2),\\
I_{26} + T_{20}  &\supseteq[46k_{1}^{2},47k_{1}^{2})= [9k_1^2, 10k_1^2),\\
I_{0}+T_{10}  &\supseteq [10k_1^2, 11k_1^2),\\
S+T_{10}  &\supseteq [11k_1^2, 14k_1^2),\\
I_{4} + T_{10}  &\supseteq [14k_1^2, 15k_1^2),\\
I_{15} + S  &\supseteq [15k_1^2, 19k_1^2),\\
I_{26} + T_{30}  &\supseteq[56k_{1}^{2},57k_{1}^{2})= [19k_1^2, 20k_1^2),\\
I_{0} + T_{20}  &\supseteq [20k_1^2, 21k_1^2),\\
S + T_{20}  &\supseteq [21k_1^2, 24k_1^2),\\
I_{4} + T_{20}  &\supseteq [24k_1^2, 25k_1^2),
\end{align*}
\begin{align*}
I_{15} + T_{10}  &\supseteq [25k_1^2, 26k_1^2),\\
I_{26} + S  &\supseteq [26k_1^2, 30k_1^2),\\
I_{0} + T_{30}  &\supseteq [30k_1^2, 31k_1^2),\\
S + T_{30}  &\supseteq [31k_1^2, 34k_1^2),\\
I_{4} + T_{30}  &\supseteq [34k_1^2, 35k_1^2),\\
I_{15} + T_{20}  &\supseteq [35k_1^2, 36k_1^2),\\
I_{26} + T_{10}  &\supseteq [36k_1^2, 37k_1^2).\qquad\qquad\qquad\ 
\end{align*}
It now follows that 
\[
\mathscr{A} + \mathscr{A} \supseteq [0, 37k_1^2).
\]
Hence
\begin{align*}
m(2,k) &\geq 37k_1^2\\
&= 37 \cdot \left \lfloor \frac{k - 2}{11}\right \rfloor^2\\
&> 37 \left(\frac{k - 2}{11} -1\right) ^2\\
&= \frac{37}{121}k^2-\frac{962}{121}k+\frac{6253}{121}\\
&= \frac{37}{121}k^2 + O(k)\qquad \text{ as }\quad k \to \infty. 
\end{align*}
Theorem~\ref{thm:m(2k)} is proved.




\section{Proof of Theorem~\ref{thm:m(dk)}}

Before we start the proof of Theorem~\ref{thm:m(dk)}, we state the following addition lemma for $m(d,k)$. Reader can find a proof of this lemma in \cite{Hsu-Jia:CombinatorialNetworks}.

\begin{lemma}\label{lemma:addition}
Given positive integers $d_{1}$, $d_{2}$, $k_{1}\ge2$ and $k_{2}\ge 2$, we have
\[
m(d_1+d_2,k_1+k_2) \geq m(d_1,k_1)m(d_2,k_2) 
\]
\end{lemma}


\begin{proof}[Proof of Theorem~\ref{thm:m(dk)}]
Let $d = 2q +r$ where $q =\displaystyle\left \lfloor \frac{d}{2}\right\rfloor$ and $k = du +v$ where $u =\displaystyle \left \lfloor \frac{k}{d}\right\rfloor$. We separate the calculation into two cases.
Case 1: If $r = 0$, then
\begin{align*}
m(d,k) &= m(2q, du +v)\\
&= m(2q, (2q)u +v)\\
&\geq m(2q, 2qu) \geq m(2, 2u)^q\\
&\geq \left(\frac{37}{121}(2u)^2+ O(u)\right)^q \\
&= \left(\frac{148}{121} \left(\frac{k-v}{d}\right) ^2+ O(u)\right)^{ \frac{d}{2}}\\
&= \left(\frac{148}{121}\right)^{ \frac{d}{2}}\left(\frac{k}{d}\right)^d + O(k^{d-1})
\end{align*}

Case 2: If $r = 1$, then
\begin{align*}
m(d,k) &= m(2q+1, du +v)\\
&= m(2q+1, (2q+1)u +v)\\
&\geq m(2q+1, 2qu + u) \geq m(2, 2u)^q \cdot m(1,u)\\
&\geq \left(\frac{37}{121}(2u)^2+ O(u)\right)^q \cdot (u+1) \\
&= \left(\frac{148}{121} u^2 + O(u)\right)^{ \frac{d-1}{2}} \cdot (u+1)\\
&= \left(\frac{148}{121}^{ \frac{d-1}{2}} u ^{d-1}+ O(u^{d-2})\right) \cdot (u+1)\\
&= \frac{148}{121}^{ \frac{d-1}{2}} u ^{d}+ O(u^{d-1})\\
&= \left(\frac{148}{121}\right)^{ \frac{d-1}{2}}\left(\frac{k}{d}\right)^d + O(k^{d-1})
\end{align*}
Hence 
\[
m(d,k) \geq \left(\frac{148}{121}\right)^{\lfloor \frac{d}{2}\rfloor}\left(\frac{k}{d}\right)^d + O(k^{d-1}).
\]
The proof of Theorem~\ref{thm:m(dk)} is complete.
\end{proof}



\section{Remarks and Open Problems}

 Let $d$ and $k$ be  positive integers. Let $n(d, k)$ denote the largest positive integer $n$ such that there exists a subset $\mathscr{A}$ of $k$ positive integers with the property that every integer in the interval $[0, n]$ is the sum of at most $d$ not necessarily distinct elements of $\mathscr{A}$. In other words, 
\[
n(d, k) = \max_{\scriptstyle \mathscr{A}\subseteq\mathbb Z^{+}\atop\scriptstyle |\mathscr{A}|=k}\{n\  |\ d \mathscr{A}\supseteq[0, n]\}.
\]
Recall that $d\mathscr A$ denotes the set of all sums of at most $d$ not necessarily distinct elements of $\mathscr A$. The computation of  $n(d, k)$ is often referred as the \emph{postage stamp problem}. The postage stamp problem is an old problem in number theory that has been studied extensively. See \cite{Hsu-Jia:CombinatorialNetworks,Selmer:1986a,Selmer:1986b} for more information. 
A simple construction shows that 
\[
n(2,k)\ge \frac14k^{2}+O(k).
\]
 Rohrbach \cite{Rohrbach:1937a} conjectured in 1937 that
\begin{equation}\label{eqn:Rohrbach's.conjecture.on.n_{alpha}(2,k)}
n(2,k)\sim\frac14{k^2},
\end{equation}
H\"ammerer and Hofmeister \cite{Hammerer-Hofmeister:1976} proved in
1976 by an explicit construction
of a $2$-basis that
\[
n(2,k)\ge \frac {5}{18}{k^2}+O(k),
\]
which disproves the conjecture of Rohrbach
(\ref{eqn:Rohrbach's.conjecture.on.n_{alpha}(2,k)}).
The  best known lower bound for $n(2,k)$ was proved by Mrose \cite{Mrose1979}
\begin{equation}\label{eqn:n(2k)}
n(2, k) \geq \frac{2}{7}k^2 + \frac{12}{7}k + O(1)\qquad  \text{as}\quad  k \to \infty.
\end{equation}
If  $d\mathscr{A}\supseteq[0, n]$ then  $d\mathscr{A}=\Z_{n+1}$. Therefore, for all positive integers $d$ and $k$ we have 
\[
m(d, k) \geq n(d, k)+1.
\]
This implies the best known lower bound for $m(2,k)$ in (\ref{eqn:m(d,2)>27}) before our result in this paper.
 Our proof uses a similar construction to one used by Torleiv Klove and Mossige used to prove the above lower bound on $n(2,k)$ in (\ref{eqn:n(2k)}).  We used a computer program to test candidates for the values that appeared in the proof as the subscripts $\mu,\ \nu$ and $\eta$.  It is likely that our result could be improved upon by a more complicated construction using a larger number of the same types of subsets.  However, testing larger constructions becomes computationally difficult, and there is a theoretical limit of $1/3$ on the leading coefficient of such a construction.  Any lower bound better than $\displaystyle\frac13k^2 + O(k)$ would be of interest.

 Other open problems include: 
\begin{enumerate}[\bf 1.]
\item  Finding a non-trivial lower bound for $m(3,k)$, $m(4,k)$, etc.

\item  For $n(d,k)$ it is known that for every positive integer $k$ the limit 
\[
\lim_{d \to \infty}{\frac{n(d,k)}{d^k}}
\]
exists, and the value is known for $k = 1,$ $2$ and $3$.  It is not known whether or not 
\[
\lim_{d \to \infty}{\frac{m(d,k)}{d^k}}
\]
exists for every k, and the value is only known for $k = 1$ and $2$. \\

\item  We may define the undirected version of our extremal function $M(d,k)$ to be the largest $M$ such that there exists of symmetric set $\mathscr{A}$ of $k$ elements and their additive inverses such that $\diam(Cay(\Z_M,\mathscr{A})) \leq d$.  Little is known about $M(d,k)$, for fixed $d$ and $k \geq 3$. \\
\end{enumerate}

\bibliographystyle{abbrv}	
\bibliography{myrefs}		

\end {document}

